Thomas et al. 2025

### 2025-01-21 IndividualStudies/AT_2025.qmd
Updates after weekly meeting

>>>>

<a href="/LipidProbe/PhosphatidicAcid.qmd" class="hover-preview">Phosphatidic Acid</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/PhosphatidicAcid_Structure.png" alt="Phosphatidic Acid" />
</span>

<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Phosphatidic Acid</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/PhosphatidylethanolamineStructure.png" alt="Phosphatidic Acid" />
</span>
